---
title: "Statistical Inference Project Part 2"
author: "Moisés R. Santos"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Basic inferential data analysis

## Purpose

Now in the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.


### Load library

```{r, warning = F, message = F}
library("dplyr")
library("ggplot2")
library("patchwork")
```

### Load the ToothGrowth data and perform some basic exploratory data analyses

```{r}
data("ToothGrowth")

head(ToothGrowth)
```


```{r}
str(ToothGrowth)
```

```{r}
summary(ToothGrowth)
```





### Provide a basic summary of the data.

```{r}
g_len_by_supp <- ggplot(ToothGrowth, aes(supp, len)) + 
  geom_boxplot(aes(fill = supp), show.legend = F) +
  xlab('Supplement type') +
  ylab('Tooth length (mm)') +
  ggtitle('Tooth length by supplement type')

g_len_by_dose <- ggplot(ToothGrowth, aes(factor(dose), len)) + 
  geom_boxplot(aes(fill = supp)) +
  xlab('Dose (mg)') +
  ylab('Tooth length (mm)') +
  ggtitle('Tooth length by dose level and supplement type')

(g_len_by_supp | g_len_by_dose)
```


### Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.


First, let's check if there is a significant difference between the 2 types of supplements: orange juice and vitamin C. In this t test, it was considered that the variances are different. 95% confidence was considered.

```{r}
t_diff_supp <- t.test(len ~ supp, ToothGrowth, var.equal = FALSE)
t_diff_supp
```
As can be seen, considering 95% confidence the null hypothesis cannot be rejected, since the p-value is greater than 0.05. So we have no evidence that there is a significant difference between the two supplements.


Now, let's see if there is a significant difference between supplements at different dosages.

#### dosage = 0.5

```{r}
t_diff_supp_0.5 <- t.test(len ~ supp, data = subset(ToothGrowth, dose == 0.5))
t_diff_supp_0.5
```
#### dosage = 1

```{r}
t_diff_supp_1 <- t.test(len ~ supp, data = subset(ToothGrowth, dose == 1))
t_diff_supp_1
```


#### dosage = 2

```{r}
t_diff_supp_2 <- t.test(len ~ supp, data = subset(ToothGrowth, dose == 2))
t_diff_supp_2
```

### Conclusions

Considering 95% confidence, from the t-tests it was possible to conclude that in general there is no significant difference between the different supplements. However, when analyzing the dosage level, there is a significant difference for 0.5 and 1 mg. It is not possible to say that for 2 mg the supplements have different growth. p-value <0.05 was considered relevant.